---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# gwasHelper

<!-- badges: start -->
<!-- badges: end -->

The goal of gwasHelper is to provide an interface to handle common downstream 
analysis of gwas summary statistics. It is build on top of the [cleansumstats](https://github.com/BioPsyk/cleansumstats)
pipeline. 

The cleansumstats provideds a consistent set of column names for postQC 
gwas summary statistics. As such, writing code for downstreams analysis is much easier.

The gwasHelper package assumes that the existence of a folder with a specific
substructure, where each subfolder is one cleaned summary statistic.


## Installation

You can install the development version of gwasHelper like so:

``` r
install_github("ararder/gwasHelper)
```



```{r example}
library(gwasHelper)
## Example code is coming!
```
